### 2017-04-04 paper/evaluation.tex
adjusted macro - rq3

Initially, we configured Maven to output all configuration variables.
The rationale is that, for each project's module, we can capture
relevant configurations and classify their parallelization level (see
Section \ref{sec:modes}) based on their values. To avoid waiting all
tests to terminate, we just run the bootstrap phase and we skip the
actual test execution.

According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
findings.

>>>>

Initially, we configured Maven to output all configuration variables.
The rationale is that, for each project's module, we can capture
relevant configurations and classify their parallelization level (see
Section \ref{sec:modes}) based on their values. To avoid waiting all
tests to terminate, we just run the bootstrap phase and we skip the
actual test execution.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.}

From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with parallel execution enabled by default.
Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.
